SU($n$) ferromagnets near the Heisenberg point

### 2020-09-22 collective_sun/sun_perturbation.tex
fixed minor error

By repeating the above process incrementally for all
$r\le r_{\t{max}}$ (starting with $r=1$), we can construct an
orthonormal basis
$\col\B_{r_{\t{max}}}\equiv\bigotimes_{r\le r_{\t{max}}}\B_r$ for the
combined manifold of all states with at most $r_{\t{max}}$ magnons.
During the construction of $\col\B_s$, an appropriate choice of
tensors $\m w$ ensures that all states $\ket{m,\m w,X}\in\col\B_s$ are
eigenstates of the base Hamiltonian $H_0$ (see Appendix
\ref{sec:eigenstates}), which is to say that $H_0$ is diagonal with
respect to $\col\B_s$.  Matrix elements of general spin operators
$\O\p{\m v,Y}$, meanwhile, take the form
\begin{align}
  \bk{\ell,\m u,X|\O\p{\m v,Y}|m,\m w,Z}
  = \bk{\ell|\O\p{\m u,X}\O\p{\m v,Y}\O\p{\m w,Z}|m}.
  \label{eq:matrix_element}
\end{align}
In order to compute these matrix elements, we simplify general
products of multi-body operators in Appendix
\ref{sec:operator_product}.

>>>>

By repeating the above process incrementally for all
$r\le r_{\t{max}}$ (starting with $r=1$), we can construct an
orthonormal basis
$\col\B_{r_{\t{max}}}\equiv\bigoplus_{r\le r_{\t{max}}}\B_r$ for the
combined manifold of all states with at most $r_{\t{max}}$ magnons.
During the construction of $\col\B_s$, an appropriate choice of
tensors $\m w$ ensures that all states $\ket{m,\m w,X}\in\col\B_s$ are
eigenstates of the base Hamiltonian $H_0$ (see Appendix
\ref{sec:eigenstates}), which is to say that $H_0$ is diagonal with
respect to $\col\B_s$.  Matrix elements of general spin operators
$\O\p{\m v,Y}$, meanwhile, take the form
\begin{align}
  \bk{\ell,\m u,X|\O\p{\m v,Y}|m,\m w,Z}
  = \bk{\ell|\O\p{\m u,X}\O\p{\m v,Y}\O\p{\m w,Z}|m}.
  \label{eq:matrix_element}
\end{align}
In order to compute these matrix elements, we simplify general
products of multi-body operators in Appendix
\ref{sec:operator_product}.
